---
title       : PS Alarms APP
subtitle    : sub title
author      : Yonatan Geremew
job         : 
framework   : revealjs  
revealjs    : {theme: sky, transition: page}
highlighter : highlight.js  
hitheme     : default      
widgets     : []            
mode        : selfcontained 
knit        : slidify::knit2slides
---

## PS Network Alarms APP 

### Data Produts Project
#### Yonatan Geremew
##### Mar 20 2015

---

## Background

- The main network elements in the Mobile Packet Switching network are the SGSN/MME and GGSN/PGW in a hybrid UMTS/LTE
network. 
- These in collaboration with other core network elements provide the data service for the customers.
- A good service provision depends on the health of these network elements, hence it is crucial to monitor the alarms.
- The 'PS Network Alarms' application is a handy tool for this important network operator activity.

---  

## Data Source

- For this application I have selected the SGSN/MME network elements. 
- The alarms are collected from three SGSNMME nodes.
- Here is the summary:
```{r, echo=FALSE}
#getwd()
ps <- read.csv("PS Alarms.csv")
ps$Alarm.ID <- as.factor(ps$Alarm.ID)
psd <- split(ps, ps$Alarm.Source)
summary(ps)
```


---  

## Graphic Comparison

<small>Using the app, we can compare which alarms are more prominent on which nodes.</small>

```{r simple-plot, fig.height = 6, fig.align = 'center', message = F, echo=FALSE}
old.par <- par(mfrow=c(1, 3))
plot(psd[[1]]$Alarm.ID, main="Alarms on SGSNMME 01",xlab='Alarm ID', 
     ylab='Count', ylim=c(0,900))
plot(psd[[2]]$Alarm.ID, main="Alarms on SGSNMME 02",xlab='Alarm ID', 
     ylab='Count', ylim=c(0,900))
plot(psd[[3]]$Alarm.ID, main="Alarms on SGSNMME 03",xlab='Alarm ID', 
     ylab='Count', ylim=c(0,900))
par(old.par)
```

---

### The APP

<small>On the PS Network alarms application you have a dropdown menu 
option for selecting anyone of the nodes to display the alarms including the option to see all the alarms on all of the nodes, as below.</small>

```{r  fig.height = 6, fig.align = 'center', message = F, echo=FALSE}
plot(ps$Alarm.ID, main="Alarms on all SGSNMME's", xlab='Alarm ID', ylab='Count', ylim=c(0,2000))
```

Thank You!


